---
title             : "Final Project Proposal - Group 1, course CSDA1000SUMA18"
shorttitle        : "Final Project Proposal"

author: 
  - name          : "Viviane Adohouannon"
    affiliation   : "1"
  - name          : "Kate Alexander"
    affiliation   : "1"
  - name          : "Juan Arangote"
    affiliation   : "1"
  - name          : "Dian Azbel"
    affiliation   : "1"
  - name          : "Vinayak Baburaj"
    affiliation   : "1"
  - name          : "Igor Baranov"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "York University School of Continious Studies"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library("papaja")
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```
# Abstract
What are the effect of the different airlines performance on airport gate utilization. 

# Introduction

# Proposed plan
Airline performance – explain what performance means:
Performance of Gate/ airline?
- Number of flights
- Number of travellers
- Number of delays coming in / going out
- Number of Cancellation

## Potential Risks

What are the threats to validity of the model?
Look for Research papers of capacity or optimizations at airport levels


## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Cost/benefit analysis
(Regression model)

# Conclusion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
